\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2013-07-08 doc/USER_MANUAL/manual_SPECFEM3D_Cartesian.tex
moved flag USE_BEST_LOCATION to the "constants.h.in" file to make it easier to change it if/when needed, and added a line about this to the users manual.

>>>>

When using this option, by default the code can locate the force source
anywhere between mesh points in order to honor its exact location; this
is more precise than using the closest GLL mesh point, but it is also a bit slower.
If needed, you can change that default behavior and force the code to use the closest
GLL mesh point instead by setting flag \texttt{USE\_BEST\_LOCATION} to \texttt{.false.} instead of \texttt{.true.} in file
\texttt{src/shared/constants.h.in} and running the \texttt{configure} script again and recompiling the code.
